A holographic approach to the six-dimensional superconformal index

### 2022-10-13 fivebranes/index.tex
section 3 stuff

\parsec[s:brkevin]
As a way to highlight the key aspects of the construction, we detail the ingredients in the simplified model of Costello's twisted $M$ theory. The relevant local calculation can be found in the appendix of \cite{}; our goal here is to simply identify the salient global features that allow one to reduce to said local calculation.

We consider the theory on $M = \text{Tot} (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
\[
0 \times C \subset \R \times \T^* C .
\]
Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$. We wish to describe the complement of the zero section $\mathring M = M - 0 \times C$.

Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $M$ with the data of a transversely holomorphic foliation (THF) \cite{DuchampKalka}.

If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $p: \R \times \T^*C \to \R_{+} \times C$ which combines the fiberwise norm with the natural bundle projection. The restriction $p| \mathring M$ equips $\mathring M$ with the structure of an $S^{2}$-bundle over $\R_{>0}\times C$. Moreover, the partial flat connection on $\R\oplus K_{C}$ induces a partially flat connection on $\mathring M$. As part of this data, each of the fiber spheres is equipped with a complex foliation of rank 1.

Compactification amounts to pushing forward a local $L_{\infty}$-algebra along $p| \mathring M$. The result is a theory with infinitely many Kaluza--Klein modes along the fiber spheres. In the holomorphic-topological setting, the Kaluza-Klein modes will be modeled by a variant of Cauchy-Riemann cohomology.

Moreover, including the flux sourced by the brane deforms this structure. The lowest lying Kaluza-Klein modes in the deformed theory are equivalent to three-dimensional Chern-Simons theory.

For sake of analogy, we think of the resulting deformation as being a twisted version of $AdS_3 \times S^2$.\footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
We first proceed before turning on the flux sourced by the brane.

The theory admits a natural `vacuum' boundary condition at $r=0$.
In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.

The `supergravity states' are, by definition, fields which satisfy the linearized equations of motion and satisfy the vacuum boundary condition except at a single point.
The linearized equations of motion are simply $(\d_{dR} + \dbar) \alpha = 0$.
Thus, up to equivalence, all solutions to the linearized equations of motion are constant in the real variable $t$, and holomorphic in $z,w$.

Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
\[
\alpha = f(w) \delta^{(r)}_{z=0}
\]
where $f$ is some holomorphic function.
Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$.
It is convenient to parameterize such boundary modifications algebraically by expressions of the form
\[
\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
\]
Linear combinations of such states form a dense subspace of all possible modifications at the boundary.

The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
The phase space at the boundary $C$ can be identified with the following cohomology
\[
\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
\]
where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation \cite{DuchampKalka}.
We refer to the section below for a reminder on this geometric structure.

The phase space is equipped with a natural symplectic form given by
\[
\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
\]
There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$

@@

We now consider the situation of backreacting some number of (twisted) fivebranes in our eleven-dimensional model.
Let $Z$ be a three-fold that the fivebranes wrap.
We also fix a rank 2 holomorphic vector bundle $W\to Z$ such that $\wedge^{2} W \cong K_{Z}$;
this condition ensures that the total space of $W$ is a Calabi-Yau five-fold. In the main body of the paper we will choose $W$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$.

@@

We will compute the pushforward using the prescription for pushing forward a $\cA^{\bu}_{F}$-module along a compatible submersion outlined in \cite{KormanThesis}. Recall that we have a THF structure on $M$, given by an involutive subbundle $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$. The situation is summarized in the diagram below.
\[
  \begin{tikzcd}
    0 \ar[r] & F_{M}\cap T_{M/Z}^{\C}\ar[r]\ar[d] & F_{M}\ar[r]\ar[d]  & \pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
    0 \ar[r] & T_{M/Z}^{\C}\ar[r] & T_{M}^{\C}\ar[r] & T_{Z}^{\C}\ar[r] & 0.
  \end{tikzcd}
\]

@@

We have a similar diagram expressing that the sphere bundle $\mathring M \to \R_{>0}\times Z$ is a map of THF manifolds when both the domain and codomain are equipped with the induced THF structures.
\[
  \begin{tikzcd}
    0 \ar[r] & F_{\mathring M}\cap T_{\mathring M/\R_{>0}\times Z}^{\C}\ar[r]\ar[d] & F_{\mathring M}\ar[r]\ar[d]  & h^{*}T_{\R_{>0}}\oplus\pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
    0 \ar[r] & T_{\mathring M/\R_{>0}\times Z}^{\C}\ar[r] & T_{\mathring M}^{\C}\ar[r] & h^{*}T_{\R_{>o}}\oplus T_{Z}^{\C}\ar[r] & 0.
  \end{tikzcd}
\]

@@

Explicitly, we set
\begin{align*}
  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} & = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}} \\
  F_{\R_{>0}\times Z} &  = T_{\R_{>0}}\oplus T^{0,1}_{Z} \text{ so }p^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z} \\
  \cA^{\bu}_{\R_{>0}\times Z}&  = \cA^{\bu}_{F _{\R_{>0}\times Z}} \text{ so }p^{*}\cA^{\bu}_{\R_{>0}\times Z} = \cA^{\bu}_{p^{*}F _{\R_{>0}\times Z}}
\end{align*}

Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.

The splitting affords an isomorphism of $C^{\infty}_{\mathring M}$-modules
\[
  \cA^{\bu}_{\mathring M}(L)\cong \cA^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L)
\]

Note that since we have a complex of locally free $C^{\infty}_{\mathring M}$-modules, the (a priori derived) functor $(p|\mathring M)_{*}$ has several nice properties. We may commute it past the tensor product above. Moreover, we may apply the functor term-wise. The result is that the pushforward is given by \surya{finish}

We now analyze the THF differential $\thfd$ on $\cA^{\bu}_{\mathring M}(L)$ under the above splitting.
\surya{finish}

@@

\begin{prop}
  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
  \beqn
  \cA^\bu_{\R_{>0}\times Z}\otimes \mathbb{R}^\bu p_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)
  \eeqn

  The BV pairing is given by
  \beqn
  \eeqn

\end{prop}

The previous result gives a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$. In particular, the result is local on $R_{>0}\times Z$. For computing the space of states, it will be useful to have a description of its global sections. For the computation of numerical invariants such as graded characters, of the space of states, a more drastic simplification is useful. Indeed, we may anticipate cohomological cancellations in the character and instead compute the character of any cochain complex that a spectral sequence whose first page is the global sections abuts to.

The global sections of the sheaf in proposition \ref{dimred} appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KamberTondeur}
\beqn
E_1^{p,q} = \Gamma \left (\R_{>0}\times Z; \cA^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q p _* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right) \right)\implies \mathbb{H}^{p+q} (\cA^\bu_{\mathring M}(L)).
\eeqn
We emphasize that no page of this spectral sequence involves cohomology with respect to the operators $D, D_{\Omega}$; these differentials are kept internal.

In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where
\beqn
M = Tot (\R\oplus \C^{2}\to \C^{3}), \ \ \ \ \ \ \mathring M = \R\times \C^2\times \C^3 \setminus (0 \times \C^3).
\eeqn

@@

\parsec[s:flux]
The second step in the construction of the backreacted geometry involves deforming the pushforward $(p| \mathring{M})_{*}\cL_{sugra}$ by a certain Maurer-Cartan element. The Maurer-Cartan element is determined by the lowest order term in the coupling between the eleven dimensional theory and the stack of fivebranes. It was argued in \cite{RSW} that the relevant coupling is given by the nonlocal interaction
\beqn\label{eqn:br1}
I_{fivebrane} = N\int_{Z} D_\Omega^{-1}\mu \vee \Omega +\cdots
\eeqn
where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)\subset \cA^{\bullet}_{F}(\vartheta_{F})$ is a component of a field in the eleven-dimensional theory which satisfies $\thfd_{\Omega} \mu = 0$.

The relevant Maurer-Cartan element is a solution to the equations of motion for the eleven-dimensional theory deformed by this interaction. After deforming with this interaction, varying with respect to $D_{\Omega}^{-1}\mu$ yields the following equation for $\gamma$
\beqn
\thfd D \gamma + D_\Omega\left (\frac{\mu}{1-\nu}\right )\wedge D \gamma = N \delta_Z.
\eeqn

@@

%\parsec[s:sugraops]
%
%By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra. 
%
%On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
%First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
%\[
%\Vect_0 (\C^5) = \{X \in \Vect(\C^5) \; | \; \div X = 0\} .
%\]
%The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
%\[
%\Omega^{1,hol}(\C^5) / {\rm Im}(\del) 
%\]
%which is, of course, equivalent to the space of closed holomorphic two-forms $\Omega^{2,hol}_{cl}(\C^5)$. 
%
%\begin{thm}[\cite{RSW}[Theorem 2.1]]
%The Taylor expansion map determines a map of $\Z/2$ graded $L_\infty$ algebras
%\[
%j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
%\]
%Furthermore, $L_{sugra}$ is equivalent as a $\Z/2$ graded $L_\infty$ algebra to $\Hat{E(5|10)}$. 
%\end{thm} 
%
%As an immediate corollary of this result we obtain by Lemma \ref{lem:localops} the following.
%
%\begin{cor}
%\label{cor:sugraops}
%Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
%There is a quasi-isomorphism of commutative dg algebras
%\[
%\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
%\]
%\end{cor}
\parsec[s:hilbertspace]
The description of the $S^{4}$ compactification of eleven dimensional supergravity obtained in the previous subsection facilitates a straightforward construciton of the Hilbert space. The compactification is described by the pro-local Lie algebra $(p|\mathring M)_{*} \cL_{sugra}$ on the seven-manifold $\R_{>0}\times Z$. We will construct the Hilbert space by applying geometric quantization ansatz to the phase space at $\infty \in \R_{>0}$.

>>>>

This procedure is implemented at the level of the $\Omega$-deformed nonminimal twist on flat space in the appendix of \cite{CostelloM5}.
%\parsec[s:brkevin]
%As a way to highlight the key aspects of the construction, we detail the ingredients in the simplified model of Costello's twisted $M$ theory. The relevant local calculation can be found in the appendix of \cite{}; our goal here is to simply identify the salient global features that allow one to reduce to said local calculation.

%We consider the theory on $M = \text{Tot} (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
%\[
%0 \times C \subset \R \times \T^* C .
%\]
%Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$. We wish to describe the complement of the zero section $\mathring M = M - 0 \times C$.

%Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $M$ with the data of a transversely holomorphic foliation (THF) \cite{DuchampKalka}.

%If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $p: \R \times \T^*C \to \R_{+} \times C$ which combines the fiberwise norm with the natural bundle projection. The restriction $p| \mathring M$ equips $\mathring M$ with the structure of an $S^{2}$-bundle over $\R_{>0}\times C$. Moreover, the partial flat connection on $\R\oplus K_{C}$ induces a partially flat connection on $\mathring M$. As part of this data, each of the fiber spheres is equipped with a complex foliation of rank 1.

%Compactification amounts to pushing forward a local $L_{\infty}$-algebra along $p| \mathring M$. The result is a theory with infinitely many Kaluza--Klein modes along the fiber spheres. In the holomorphic-topological setting, the Kaluza-Klein modes will be modeled by a variant of Cauchy-Riemann cohomology.

%Moreover, including the flux sourced by the brane deforms this structure. The lowest lying Kaluza-Klein modes in the deformed theory are equivalent to three-dimensional Chern-Simons theory.

%For sake of analogy, we think of the resulting deformation as being a twisted version of $AdS_3 \times S^2$.\footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
%We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
%We first proceed before turning on the flux sourced by the brane.

%The theory admits a natural `vacuum' boundary condition at $r=0$.
%In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.

%The `supergravity states' are, by definition, fields which satisfy the linearized equations of motion and satisfy the vacuum boundary condition except at a single point.
%The linearized equations of motion are simply $(\d_{dR} + \dbar) \alpha = 0$.
%Thus, up to equivalence, all solutions to the linearized equations of motion are constant in the real variable $t$, and holomorphic in $z,w$.

%Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
%\[
%\alpha = f(w) \delta^{(r)}_{z=0}
%\]
%where $f$ is some holomorphic function.
%Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$.
%It is convenient to parameterize such boundary modifications algebraically by expressions of the form
%\[
%\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
%\]
%Linear combinations of such states form a dense subspace of all possible modifications at the boundary.

%The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
%The phase space at the boundary $C$ can be identified with the following cohomology
%\[
%\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
%\]
%where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation \cite{DuchampKalka}.
%We refer to the section below for a reminder on this geometric structure.

%The phase space is equipped with a natural symplectic form given by
%\[
%\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
%\]
%There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
%The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$

@@

We now carry out the above procedure to backreact fivebranes in our eleven-dimensional model.
Let $Z$ be a three-fold that the fivebranes wrap.
We also fix a rank 2 holomorphic vector bundle $W\to Z$ such that $\wedge^{2} W \cong K_{Z}$;
this condition ensures that the total space of $W$ is a Calabi-Yau five-fold. In the main body of the paper we will choose $W$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$.

@@

We will compute the pushforward using the prescription for pushing forward a $\cA^{\bu}_{F}$-module along a compatible submersion outlined in \cite{KormanThesis}. Recall that we have a THF structure on $M$, given by an involutive subbundle $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$. The situation is summarized in the diagram below.
\[
  \begin{tikzcd}
    0 \ar[r] & F_{M}\cap T_{M/Z}\ar[r]\ar[d] & F_{M}\ar[r]\ar[d]  & \pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
    0 \ar[r] & T_{M/Z}\ar[r] & T_{M}\ar[r] & T_{Z}\ar[r] & 0.
  \end{tikzcd}
\]
We note that all vector bundles in the above diagram are complexified.

@@

We have a similar diagram expressing that the sphere bundle $\mathring M \to \R_{>0}\times Z$ is a map of THF manifolds when both the domain and codomain are equipped with the induced THF structures.
\[
  \begin{tikzcd}
    0 \ar[r] & F_{\mathring M}\cap T_{\mathring M/\R_{>0}\times Z}\ar[r]\ar[d] & F_{\mathring M}\ar[r]\ar[d]  & h^{*}T_{\R_{>0}}\oplus\pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
    0 \ar[r] & T_{\mathring M/\R_{>0}\times Z}\ar[r] & T_{\mathring M}\ar[r] & h^{*}T_{\R_{>o}}\oplus T_{Z}\ar[r] & 0.
  \end{tikzcd}
\]

@@

Explicitly, we set
\[
  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} & = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}
\]
for the complex resoling functions on $\mathring M$ constant in the directions of $F_{\mathing M}$ that are tangent to the fibers of $(p|\mathring M)$.

Likewise, we let
\[
  F_{\R_{>0}\times Z} = T_{\R_{>0}}\oplus T^{0,1}_{Z}
\] be the subbundle of the tangent bundle of the base locally spanned by $\del_{}t, \del_{z_{i}}$ and $(p|\mathring M)^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}$ the pullback, which is a subbundle of $T_{\mathring M}$. We will let $\cA^{\bu}_{\R_{>0}\times Z}&  = \cA^{\bu}_{F _{\R_{>0}\times Z}}$ denote the THF complex resolving functions constant along the elaves of this foliation on the base.

Our goal is to describe the derived pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.

We first note that the splitting gives us an isomorphism of $C^{\infty}_{\mathring M}$-modules
\begin{align*}
  \cA^{\bu}_{\mathring M}(L) & \cong \cA^{\bu}_{(p|\mathring M)^{*}F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\

                         & \cong (p|\mathring M)^{*}\cA ^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\

\end{align*}

where we have just used that pullback commutes with taking the exterior power. Here, the tensor product is take in $C^{\infty}_{\mathing M}$-modules.

%Note that since we have a complex of locally free $C^{\infty}_{\mathring M}$-modules, the derived pushforward along $(p|\mathring M)_{*}$ coincides with the orinary pushforward. Moreover since the derived pushforward commutes with tensor product, we have that the $(p|\mathring M)_{*}\cL_{sugra}$ is given by

By the projection formula, there is an isomorphism of $C^{\infty}_{\R_{>0}\times Z}$-modules
\[
\cA ^{\bu}_{\R_{>0}\times Z}\otimes_{C^{\infty}_{\R_{>0}\times Z}} (p|\mathring M)_{*}\cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \to (p|\mathring M)_{*}\left ( (p|\mathring M)^{*}\cA ^{\bu}_{\R_{>0}\times Z}\otimes_{C^{\infty}_{\mathring M}} \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \right )\]

%Now the unit of the adjunction between inverse and direct image of $C^{\infty}_{M}$-modules induces a map
%\[
%  \cA^{#}_{\R_{>0}\times Z} \to (p|\mathring M)_{*}(p|\mathring M)^{*}\cA ^{#}_{\R_{>0}\times Z}
%\]

 The left hand side of the above isomorphism has a canonical $\cA ^{#}_{\R_{>0}\times Z}$-modules structure. It remains to discuss compatibility with the differential along the base. The compatibility condition is expressed through the observation that the pro-vector bundle \[(p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\] will have the structure of a partial flat connection defined along the leaves of $F_{\R_{>0}\times Z}$. We can construct such a connection from analyzing the behavior of the THF differential $\thfd$ under the splitting.

 The THF differential induces a derivation of total degree 1 on the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ so it is determined by its restrictions

\[\thfd_{i} :  (p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \to \cA^{i}_{\R_{\geq >0} \times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M)_{*} \cA^{\bullet-i+1}_{\mathring M/\R_{>0}\times Z}(L).\]

We may understand the first few terms, along with the relations implied by $\thfd^{2} = 0$:
\begin{itemize}
  \item The first term \[\thfd_{0} : (p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to (p|\mathring M_{*})\cA^{\bullet+1}_{\mathring M/\R_{>0}\times Z}(L)\] is the internal differential.

  \item The second term \[\thfd_{0} : (p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to \cA^{1}_{\R_{\geq 0}\times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\] is a partial connection. However, it is not flat. Rather the failure for flatness is captured by \[ \thfd_{1}^{2} + [\thfd_{0}, \thfd_{2}] = 0 \] where \[ \thfd_{2} : (p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to \cA^{2}_{\R_{\geq 0}\times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M_{*})\cA^{\bullet-1}_{\mathring M/\R_{>0}\times Z}(L) \] is a nullhomotopy.
\end{itemize}
In particular, $\thfd_{1}$ induces a partial flat connection along $F_{\R_{>0}\times Z}$ the hypercohomology \[\mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right )\].

In \cite{KormanThesis} it is shown that though the above decomposition depends on the choice of splitting $\mathring \sigma$ initially chosen, the flat connection induced by $\thfd_{1}$ on the hypercohomology does not.

@@

\begin{prop}\label{p:dimred}
  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
  \beqn
  \cA^\bu_{\R_{>0}\times Z}\otimes \mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)
  \eeqn

  with the $\cA^{\bullet}_{\R_{>0}\times Z}$-module structure coming from the partial flat connection induced by $\thfd_{1}$.
\end{prop}

The BV pairing naturally descends to the above complex of sheaves. We can explicitly describe it as follows. First note that the fiber of $\mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)$ at $(t,p)\in \R_{>0}\times Z$ can be computed as the cohomology of the complex
\[
H^{\bullet}\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right ).
\]

Moreover, the deformation retraction along the fibers $(R\times \C^{2})_{(t,p)}- 0 \to S^{4}_{(t,p)}$ induces a quasi-isomorphism
\[
\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong
\]
Thus, we have a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$. In particular, the result is local on $R_{>0}\times Z$.

For computing the space of states, it will be useful to have a description of its global sections. The global sections of the sheaf in proposition \ref{p:dimred} appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KamberTondeur}
\beqn
E_1^{p,q} = \Gamma \left (\R_{>0}\times Z; \cA^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q(p|\mathring M) _* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right) \right)\implies \mathbb{H}^{p+q} (\cA^\bu_{\mathring M}(L)).
\eeqn\label{thfss}
We emphasize that no page of this spectral sequence involves cohomology with respect to the operators $D, D_{\Omega}$; these differentials are kept internal.

The $E_{2}$ page is similarly given by flat sections with respect to $\thfd_{1}$
\beqn
E_2^{p,q} = \Gamma_{\thfd_1} \left (\R_{>0}\times Z; \cA^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q (p|\mathring M) _* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right) \right)
\eeqn

In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where
\beqn
M = Tot (\R\oplus \C^{2}\to \C^{3}), \ \ \ \ \ \ \mathring M = \R\times \C^2\times \C^3 \setminus (0 \times \C^3).
\eeqn
In this case, the above spectral sequence clearly degenerates at the $E_{2}$-page.

@@

\parsec[s:flux]
The second step in the construction of the backreacted geometry involves deforming the pushforward $(p| \mathring{M})_{*}\cL_{sugra}$ by a certain Maurer-Cartan element. The Maurer-Cartan element is determined by the lowest order term in the coupling between the eleven dimensional theory and the stack of fivebranes. It was argued in \cite{RSW} that the relevant coupling is given by the nonlocal interaction
\beqn\label{eqn:br1}
I_{fivebrane} = N\int_{Z} D_\Omega^{-1}\mu \vee \Omega +\cdots
\eeqn
where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)\subset \cA^{\bullet}_{F}(Q)$ is a component of a field in the eleven-dimensional theory which satisfies $\thfd_{\Omega} \mu = 0$.

The relevant Maurer-Cartan element is a solution to the equations of motion for the eleven-dimensional theory deformed by this interaction. After deforming with this interaction, varying with respect to $D_{\Omega}^{-1}\mu$ yields an equation for $\gamma$ that to linear order reads:
\beqn
\thfd D \gamma  = N \delta_Z.
\eeqn

The existence of a solution to this equation is a strong constraint on the THF manifold $M$. The relevant consequence for us is that it implies the degeneration of the spectral sequence \ref{thfss} at the $E_{2}$-page.

@@

%\parsec[s:sugraops]
%
%By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra. 
%
%On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
%First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
%\[
%\Vect_0 (\C^5) = \{X \in \Vect(\C^5) \; | \; \div X = 0\} .
%\]
%The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
%\[
%\Omega^{1,hol}(\C^5) / {\rm Im}(\del) 
%\]
%which is, of course, equivalent to the space of closed holomorphic two-forms $\Omega^{2,hol}_{cl}(\C^5)$. 
%
%\begin{thm}[\cite{RSW}[Theorem 2.1]]
%The Taylor expansion map determines a map of $\Z/2$ graded $L_\infty$ algebras
%\[
%j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
%\]
%Furthermore, $L_{sugra}$ is equivalent as a $\Z/2$ graded $L_\infty$ algebra to $\Hat{E(5|10)}$. 
%\end{thm} 
%
%As an immediate corollary of this result we obtain by Lemma \ref{lem:localops} the following.
%
%\begin{cor}
%\label{cor:sugraops}
%Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
%There is a quasi-isomorphism of commutative dg algebras
%\[
%\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
%\]
%\end{cor}
\parsec[s:hilbertspace]
The description of the $S^{4}$ compactification of eleven dimensional supergravity obtained in the previous subsection facilitates a straightforward construciton of the Hilbert space. The compactification is described by the pro-local Lie algebra $(p|\mathring M)_{*} \cL_{sugra}$ on the seven-manifold $\R_{>0}\times Z$ in proposition \ref{p:dimred}. We will construct the Hilbert space by applying geometric quantization ansatz to the phase space at $\infty \in \R_{>0}$.
